Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-21 paper/v2/paper-edited.tex
fix formatting issues

Total compilation for the largest datacenter is less than 9 minutes total. Unlike the datacenter policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases. Compilation for the largest backbone network, takes less than 3 minutes total. The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.

>>>>

Total compilation for the largest datacenter is less than 9 minutes total. Unlike the datacenter policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases. Compilation for the largest backbone network, takes less than 3 minutes total. The inclusion of both more preferences and more neighboring ASes in the backbone policy increases the size of the resulting PGIR, which in turn leads to PGIR construction and minimization taking proportionally more time.
